An Infinite de Bruijn Sequence

### 2016-12-26 paper.tex
added specifically

This observation lead us to look at the reverse of the prefer-max sequence. The structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.

>>>>

This observation lead us to look at the reverse of the prefer-max sequence. Specifically, the structure identified in Theorem~\ref{thm:onion} means that if we somehow manage to construct the sequence backwards, we do not have to specify $k$ ahead of time because we can go on indefenitiley while $k$ grows in layers: we first write $0^n$, then a word whose substrings of length $n$ are $\{0,1\}^n$, then extend to $\{0,1,2\}^n$, and so on.
